---
title: "Leaf Decomposition Across Multiple Stressor Gradients: A Comparative Study of the Boye and Kinzig Catchments, Germany"
author:
  - name: "Ikenna Stephen Agube"
    affiliation: "University of Duisburg-Essen, Environmental Toxicology"
    matriculation: "3199575"
    email: "agubeikenna.stephen@gmail.com"
date: "`r format(Sys.Date(), '%d %B %Y')`"
output:
  html_document:
    toc: true
    toc_depth: 4
    toc_float: true
    number_sections: true
    highlight: tango
    fig_caption: true
    theme: flatly
  pdf_document:
    toc: true
    toc_depth: 4
    number_sections: true
  word_document:
    toc: true
    toc_depth: 4
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo    = TRUE,
  warning = FALSE,
  message = FALSE,
  fig.width  = 8,
  fig.height = 5,
  dpi     = 300
)
```

---

# Title Page {-}

| | |
|---|---|
| **Student** | Ikenna Stephen Agube |
| **Matriculation number** | 3199575 |
| **Programme** | M.Sc. Environmental Toxicology |
| **University** | University of Duisburg-Essen |
| **1st Examiner** | Dr. V.C. Schreiner — Universitätsstr. 5, 45141 Essen |
| **2nd Examiner** | Dr. A. Lorenz — Fakultät für Biologie (Aquatische Ökologie), Universitätsstr. 5, D-45141 Essen |
| **Thesis start** | 01 May 2026 |
| **Submission deadline** | 01 November 2026 |

---

# Load Packages

```{r packages}

```

---

# Set Working Directory

```{r working-directory}
# Portable working directory — detects script location automatically
if (requireNamespace("rstudioapi", quietly = TRUE) && rstudioapi::isAvailable()) {
  script_dir <- dirname(rstudioapi::getActiveDocumentContext()$path)
} else {
  script_dir <- getSrcDirectory(function() {})
}
data_dir <- normalizePath(file.path(script_dir, "..", "data", "processed"),
                          mustWork = FALSE)
setwd(data_dir)
message("Working directory: ", getwd())
```

---

# Load Data

```{r load-data}

```

---

# Data Cleaning

```{r data-cleaning}

```

---

# Results

##

```{r results}

```

---

# Discussion

---

# Session Info

```{r session-info}
sessionInfo()
```
